\bf Faster Neural Machine Translation Inference

### 2018-02-06 fast-beam/fast-beam.tex
fast beam paper

The output layer of most deep learning models consist of the following steps
\begin{enumerate}
   \item \vspace{-2 mm} multiplication of the input with the weight vector $p = w x$
   \item \vspace{-2 mm} addition of a bias term to the resulting scores $p = p + b$
   \item \vspace{-2 mm} applying the activation function, most commonly softmax $ p_i = \exp(p_i) / \sum \exp(p_i) $
   \item \vspace{-2 mm} a search for the best output class, and probability if necessary $\argmax_i p_i$
\end{enumerate}

@@

\begin{algorithm}
\begin{algorithmic}
\Procedure{Mini-Batching}{}
%\REQUIRE source sentence $s$, translation options
\While{more input} 
  \State Create batch
  \State Encode(batch)
  \While{batch is not empty} 
    \State Decode(batch)
    \For{each sentence in batch}
      \If{translation is complete}
        \State Remove sentence %from batch
      \EndIf
    \EndFor
  \EndWhile
\EndWhile

@@

\Procedure{Encode}{}
\While{more input} 
  \State Create encoding batch $b$
  \State Encode($b$)
  \State Add $b$ to queue
\EndWhile

@@

\State create batch $b$ from queue
\While{$b$ is not empty}
  \State Decode($b$)
  \State Replace completed sentences with new sentence from queue
\EndWhile

@@

>>>>

The output layer of most deep learning models consist of the following steps
\begin{enumerate}
   \item \vspace{-2 mm} multiplication of the input with the weight vector $p = w x$
   \item \vspace{-2 mm} addition of a bias term to the resulting scores $p = p + b$
   \item \vspace{-2 mm} applying the activation function, most commonly softmax $ p_i = \exp(p_i) / \sum \exp(p_i) $
   \item \vspace{-2 mm} a beam search for the best (or n-best) output classes $\argmax_i p_i$
\end{enumerate}

@@

\begin{algorithm}
\begin{algorithmic}
\Procedure{Mini-Batching}{}
%\REQUIRE source sentence $s$, translation options
\While{more input} 
  \State Create batch $b$
  \State Encode($b$)
  \While{batch is not empty} 
    \State Decode($b$)
    \ForAll{sentence $s$ in $b$}
      \If{translation is complete}
        \State Remove $s$ from $b$
      \EndIf
    \EndFor
  \EndWhile
\EndWhile

@@

\Procedure{Encode}{}
\While{more input} 
  \State Create encoding batch $b$
  \State Encode($b$)
  \State Add $b$ to queue $q$
\EndWhile

@@

\State create batch $b$ from queue $q$
\While{$b$ is not empty}
  \State Decode($b$)
  \ForAll{sentence $s$ in $b$}
    \If{translation is complete}
      \State Replace $s$ with $s'$ from $q$
    \EndIf
  \EndFor
\EndWhile

@@

\begin{table}
\begin{center}
\small
\begin{tabular}{|l|r|r|} \hline
		& Baseline	& Fused \\ \hline
\multicolumn{3}{|c|}{\emph{Beam size 1}}	\\ \hline	
Multiplication 	& 25.62 	& 26.47 (+3.3\%) \\ \hline
Add bias 	& 4.98		&  \\ 
Softmax 	& 12.81		& 7.94 (-76.9\%)\\
Beam search	& 16.64		&  \\ \hline
\multicolumn{3}{|c|}{\emph{Beam size 5}}	\\ \hline	
Multiplication 	& 112.9 	& 115.04 (+1.9\%) \\ \hline
Add bias 	& 23.66		&  \\ 
Softmax 	& 56.61		& 67.58 (-56.5\%)\\
Beam search	& 75.12		&  \\ \hline
\end{tabular}
\end{center}
\caption{Time taken in sec (Europarl)}
\label{tab:fused-breakdown}
\end{table}
